Estimating duration in the presence of misclassification

### 2024-03-19 conclusion.tex
Overleaf comments and rewrite 7.1

In \cref{E-transmission}, I found that this it is possible, developing two models that can infer incidence and transmission from prevalence surveys.
One model was phenomenological in nature and the other mechanistic.
The phenomenological approach, based on the backcalculation framework, provides estimates of incidence and makes fewer assumptions about the infection process; however, the estimates are very uncertain.
The mechanistic approach, based on an SIR-type compartmental model, reduces the uncertainty and allows estimation of the components of transmission by making stronger assumptions about the infection process.
These results highlighted the heterogeneity across regions and age groups in England.

@@

The feasibility of jointly modelling duration and incidence was not investigated in this thesis.
The model for duration in \cref{E-perf-test,E-imperf-test} allowed estimation of the total number of infections in the cohort but assumed these occurred uniformly over the duration of the survey.
If, rather than assuming uniformity, the time of incidence was estimated, this would be a form of incidence estimation.
The issue of including covariates to control for non-response bias, encountered in \cref{E-transmission}, as well as the parameterization of the shape of the incidence curve would be major challenges in this extension.
The basis of such a model could be existing modelling frameworks~\autocite[e.g.][]{taffeJoint,haySerosolver}.
These frameworks addressed the challenges by: taking approximations (\eg empirical Bayes), having smaller sample sizes, or using high-performance computing.
However, the CIS is larger and incidence estimation desired at a more granular level than previously encountered.
Furthermore, high-performance computing cannot be used within the SRS.

>>>>

In \cref{E-transmission}, I found that this it is possible, developing two models that can infer incidence and transmission from prevalence surveys.
One model was phenomenological in nature and the other mechanistic.
The phenomenological approach, based on the backcalculation framework, provides estimates of incidence and makes fewer assumptions about the infection process; however, the estimates are very uncertain.
The mechanistic approach, based on an SEIR-type compartmental model, reduces the uncertainty and allows estimation of the components of transmission by making stronger assumptions about the infection process.
Both sets of results highlighted the heterogeneity across regions and age groups in England.
The choice of modelling approach should depend on the situation.
The phenomenological approach is more robust when there are high levels of uncertainty; for example, early in an outbreak or in the presence of new variants the infectious period duration may not be known.
However, the mechanistic approach provides more information.
Where possible, both methods should be implemented; discrepancies between results may highlight deficiencies in modelling assumptions.

@@

A natural extension of the work in this thesis would be a joint model of duration and incidence.
Such a model poses both identifiability and computational challenges.
The model for duration in \cref{E-perf-test,E-imperf-test} allowed estimation of the total number of infections in the cohort but assumed these occurred uniformly over the duration of the survey.
If, rather than assuming uniformity, a distribution for the infection episode start times was estimated, this would be a form of incidence estimation.
Previous studies~\autocite[e.g.][]{bacchettiNonparametric} have suggested that a joint model would be unidentifiable; however, CIS data contains information on the number of individuals that were never infected which may be sufficient to resolve this issue.
The issue of including covariates to control for non-response bias, encountered in \cref{E-transmission}, as well as the parameterization of the shape of the incidence curve would be major challenges in this extension.
The basis of such a model could be existing modelling frameworks~\autocite[e.g.][]{taffeJoint,haySerosolver}.
These frameworks addressed the challenges by: taking approximations (\eg empirical Bayes), having smaller sample sizes, or using high-performance computing.
However, the CIS is larger and incidence estimation desired at a more granular level than previously encountered.
Furthermore, high-performance computing cannot be used within the SRS.

### 2024-03-19 transmission.tex
Overleaf comments and rewrite 7.1

The first approach, which I call the \emph{incidence-inferred} approach, is a single statistical model where incidence is inferred, with prevalence as a derived quantity.
The basis of the statistical model, in a Bayesian framework, would be as follows.
\begin{align}
    \vec{Z} \mid \vec{\phi} &\dist g_Z(\vec{\phi}) \\
    \vec{P_{i}} &= \matr{S} \vec{Z}_i \\
    Y_{i,t} \mid \vec{P} &\dist \BB(n_{i,t}, P_{i,t})
\end{align}
where $\vec{Z}$ is a vector of incidence proportion for each strata and day defined by some model $g$ with parameters $\vec{\phi}$; $P_{i,t}$ is the prevalence in stratum $i$ on day $t$; $\matr{S}$ is the survival matrix defined in \cref{E-inc-prev:eq:Smatrix}; $Y_{i,t}$ is the number of positive tests in stratum $i$ on day $t$; and $n_{i,t}$ is the number of tests in stratum $i$ on day $t$.
The model $g_Z$ would be specified to share information across time and/or strata.
This both helps stabilise the estimation (see \cref{intro:sec:disease-model}) and allows borrowing of information across strata.
Borrowing information is required because some strata and time combinations have few positives (fewer than five per day).
The relationship between $P$ and $Z$ is from \cref{E-inc-prev:eq:EPt-matrix}, although dividing both sides by $\Npop$ to have the values in terms of incidence proportion and prevalence rather than incidence and number of prevalent individuals.

The second approach, which I call the \emph{prevalence-inferred} approach takes a two-step approach.
First, it uses the statistical model from \cref{E-biology-data:sec:MRP} to estimate prevalence.
Then, it transforms the posterior distribution of prevalence to a posterior distribution of incidence using the forward substitution as in \cref{E-inc-prev:eq:forward-substitute}.
At a high-level, the statistical model is:
\begin{align}
    \vec{P} \mid \vec{\phi} &\dist g_P(\vec{\phi}) \\
    Y_{i,t} \mid \vec{P} &\dist \BB(n_{i,t}, P_{i,t})
\end{align}
where $g_P$ is analogous to $g_Z$ in providing a joint prior for the prevalence in each stratum and day combination.
Step 2 is...

@@

The incidence-inferred approach is more parsimonious in being a single step procedure.
However, it poses several pragmatic challenges which means I favour the prevalence-inferred approach.
Here I explain that further developments, beyond the scope of this thesis, would be required to use the incidence-inferred approach with a suitable $g_Z$ within the computational constraints of the SRS.

Denote the quantity to be inferred at time $t$ in strata $i$ as $\pi_{i,t}$.
That is, under the incidence-inferred approach, $\pi_{i,t}$ is the incidence proportion, and under the prevalence-inferred approach, $\pi_{i,t}$ is the prevalence.

The chosen approach should have the following properties.
\begin{enumerate}
    \item The smoothing model, $g_Z$ or $g_P$, over time should penalise changes from continuous exponential growth of $\pi$ over time.
        Penalizing changes from continuous exponential growth is a natural formulation because mechanistic models predict exponential growth over short periods of time.
        Furthermore, such penalization has previously been shown to improve estimates of SARS-CoV-2 prevalence by balancing over and under-fitting~\autocite{ealesAppropriately}. Used by CIS (section 3.?).
    \item Limit estimates to epidemiologically and biologically plausible values.
        That is, incidence proportion and prevalence should be in the interval $[0, 1]$.
        % While incidence proportion can theoretically be greater than 1, this would imply that some individuals were infected multiple times in a day which is not biologically plausible.
    \item Have sufficient parameters to incorporate all necessary covariates to correct for non-response bias.
    \item Borrow information across the different covariates.
        The borrowing should penalize changes in the distribution of incidence/prevalence across strata in the same geographic region being constant.
        A constant distribution is predicted by the theoretical study of epidemics, for example the dynamics of stratified, mechanistic transmission models (such as the one introduced in \cref{E-SEIR:sec:structured-populations}) over short periods of time with negligible behavioural and immunity changes.
    \item Be computationally efficient.
        The model will be fit to granular data and therefore needs to be run within the SRS, with its computational limitations (see \cref{E-biology-data:sec:SRS}).
\end{enumerate}

Properties 1 and 2 suggest a model of the form $\logit(\pi_{i,t}) = g(i, t)$, where $g$ is a function with changes in the first derivative penalized w.r.t.\ $t$ (\ie changes away from linear are penalised).
The $\logit$ link function both limits $\pi_{i,t}$ to the interval $[0, 1]$, and logit-linear growth approximates exponential growth for small $\pi_{i,t}$~\autocite{ealesAppropriately}.
Combined with property 4, the form of $g$ the null model is $g(i, t) = a_0 + a_t t + f(i)$ where $a_0$ and $a_t$ are model parameters and $f$ is a function to be specified; that is, changes away from this model should be penalized.

@@

INLA-based inference can only be applied to LGMs (\emph{Latent Gaussian Models})~\autocite{rueINLAseminar,rueINLA,martinoINLAtutorial}; see \cref{E-transmission:sec:INLA} for further details on INLA.

@@

Therefore, using the INLA approximation while satisfying the other desirable properties requires that $g$ predicts prevalence, not incidence proportion.
Hence, I adopt the prevalence-inferred approach.

@@

Now I explain how I extended the MRP model introduced in \cref{E-biology-data:sec:MRP} to implement the prevalence-inferred approach.

First, I draw a sample of 500 prevalence time series in each stratum from the approximate posterior distribution (using the procedure described in \cref{transmission:sec:INLA:posterior}).
For each stratum, I use the relationship in \cref{E-inc-prev:eq:EPt} to calculate the incidence proportion at each time point.
I consider the relationship between incidence and prevalence within a stratum to be deterministic, as \cref{E-inc-prev:sec:observation-process} justifies, that is the estimate of the incidence is negligibly affected by approximating the distribution $\vec{P} \mid \vec{Z}$ by its mean.
I solve this system using forward substitution, calculating the value of $Z_t$ in \cref{E-inc-prev:eq:forward-substitute} sequentially for $t = 1, \dots, T$.
\Cref{E-inc-prev:eq:forward-substitute} is repeated here for convenience:
\begin{align}
Z_t
&= \frac{P_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= P_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{transmission:eq:forward-substitute}
\end{align}
% \Cref{E-inc-prev:eq:EPt}, considered across different values of $t$, can be written as $\vec{P} = \matr{S} \vec{Z}$, where: $\vec{P}$ is a vector of the number of prevalent individuals at each time point in the stratum; $\matr{S}$ is a matrix formed from the survival function, as defined below; and $\vec{Z}$ is a vector of the incidence at each time point in the stratum.
Dividing each side by the total number of individuals in each stratum transforms the number of prevalent individuals to prevalence and incidence to incidence proportion.

Violation of assumptions in various parts of this procedure can lead to the second term in \cref{transmission:eq:forward-substitute} to be greater than the first, giving negative incidence.
In this case, the incidence prior to day $t$ imply that the prevalence on day $t$ is higher than that predicted by the fitted regression model for this strata/day combination.
There are two sets of assumptions which are most likely to be violated.
The first set of assumptions is in constructing survival matrix, $\matr{S}$, which is assumed to be known with no uncertainty in this procedure.
However, \cref{E-imperf-test} showed that the estimate of $S(t)$ is sensitive to assumptions made, such as the assumed $\psens$ and strength of priors used.
The second set of assumptions are in specifying the statistical model used to estimate prevalence, for example the form of the smoothing used.
In particular, the prior for $\pi_P$ places non-zero mass on prevalence values which imply negative incidence under the other model assumptions.

For $\vec{P} = \matr{S} \vec{I}$ to have a unique solution, $\vec{I}$ and $\vec{P}$ need the same dimension.
However, I am using a period of prevalence which starts after the first infections.
These prior infections will still contribute to the prevalence.
I assume that the incidence up to and including the first day of prevalence data, at $t = 1$, is constant at $I_0$.
Therefore, $P_1 = I_0 \sum_{i=1}^{\dmax} S(i)$ and $I_0 = P_1 / \sum_{i=1}^{\dmax} S(i)$.
For day $t$, the contribution of the incidence for $t < 1$ can be calculated as $P'_t = I_0 \sum_{i=t+1}^{\dmax} S(i)$.
Subtracting $\vec{P'}$ from $\vec{P}$ before applying the forward solving procedure accounts for the contribution of the incidence prior to the first day of prevalence data.

Once the incidence proportion in each stratum have been calculated using this procedure, I poststratify it to the CIS target population and subpopulations of interest.
This is done using the methodology explained in \cref{E-biology-data:sec:MRP}.

@@

During November, incidence starts rising, with regional heterogeneity in the timing of when this occurs (see \cref{transmission:fig:backcalc-regions}).
The most explored explanation for this is the emergence of the Alpha variant, which was more transmissible than previous variants and emerged at different times across the country~\autocite{walkerTracking,daviesEstimated,lythgoeLineage}.
There is evidence that when incidence starts increasing is correlated with when the Alpha variant's spread (see \cref{transmission:fig:backcalc-alpha}).
A second peak occurs in late December or early January in all regions; this second peak is larger than the first in all regions except the Northern three (North East, North West, and Yorkshire and the Humber).
\begin{figure}
    \includegraphics{transmission/backcalc-regions}
    \caption[Incidence estimated using backcalculation by region]{%
        Incidence proportion for all of England (A) and its component regions.
        Regions are split into broad groupings of three regions each: Northern (B), Midlands (C), and Southern (D).
        Yorkshire and the Humber is labelled as Yorkshire for brevity.
    }
    \label{transmission:fig:backcalc-regions}
\end{figure}
\begin{figure}
    \includegraphics{transmission/backcalc-alpha}
    \caption[Correlation of the emergence of Alpha and minimum incidence.]{%
        x-axis: time that S-gene target failure, a marker of the Alpha variant, is estimated to start increasing from baseline by region among CIS test results; from \textcite[table S3]{walkerTracking}.
        y-axis: posterior median and 95\% CrI of the date of minimum incidence in November or early December in each region.
        Linear regression line shown.
    }
    \label{transmission:fig:backcalc-alpha}
\end{figure}

@@

Various alternative inference techniques could be considered.
If the infection process is considered a Poisson process (defined in \cref{E-inc-prev:sec:poisson-process}), then, conditional on the process's intensity, there is independence between individuals' infection status.
The conditional independence implies the incidence proportion and prevalence are the mean of many independent Bernoulli variables.
Therefore, the Central Limit Theorem implies they are approximately normally distributed.
Exploiting this property could enable efficient approximations to the posterior.
For example, a Laplace approximation or variational inference.
Further work to check the quality of these approximations, is required.

>>>>

The first approach, which I call the \emph{incidence-inferred} approach, is a single statistical model where incidence is inferred, with prevalence as a derived quantity.
The basis of the statistical model, in a Bayesian framework, would be as follows.
\begin{align}
    \vec{Z} &\dist F_Z \\
    P_{i,t}  &= \sum_{k=0}^{d_\text{max}-1} Z_{i,t-k} S(k+1) \\
    \rho &\dist F_\rho \\
    Y_{i,t} \mid \vec{P}, \rho &\dist \BB(n_{i,t}, P_{i,t}, \rho)
\end{align}
where $\vec{Z}$ is a vector such that $Z_{i,t}$ is the incidence proportion in stratum $i$ on day $t$, and has prior $F_Z$; $P_{i,t}$ is the prevalence in stratum $i$ on day $t$; $\rho$ is the overdispersion parameter of the beta-binomial distribution with prior $F_\rho$; $Y_{i,t}$ is the number of positive tests in stratum $i$ on day $t$; and $n_{i,t}$ is the number of tests in stratum $i$ on day $t$.
Fitting this model to a prevalence survey such as the CIS (\eg using MCMC) gives a posterior distribution of $\vec{Z}$, the target of inference.

The relationship between $P$ and $Z$ is from \cref{E-inc-prev:eq:EPt}, although dividing both sides by $\Npop$ to have the values in terms of incidence proportion and prevalence rather than incidence and number of prevalent individuals.

Specifying $F_Z$ would depend on the application of the approach, but should consider the need to provide structure to stabilise the problem (see \cref{E-intro:sec:disease-model}).
In the context of the CIS, it needs to allow borrowing information across time and/or strata; this is required because some stratum and time combinations have few positives (fewer than five per day).

The second approach, which I call the \emph{prevalence-inferred} approach takes a two-step approach.
First, it uses the statistical model from \cref{E-biology-data:sec:MRP} to estimate prevalence.
Then, it transforms the posterior distribution of prevalence to a posterior distribution of incidence using the forward substitution as in \cref{E-inc-prev:eq:forward-substitute}.
At a high-level, the statistical model is:
\begin{align}
    \vec{P}  &\dist F_P \\
    \rho &\dist F_\rho \\
    Y_{i,t} \mid \vec{P}, \rho &\dist \BB(n_{i,t}, P_{i,t}, \rho)
\end{align}
where $F_P$ is analogous to $F_Z$ in providing a joint prior for the prevalence in each stratum and day combination, and all other notation is as in the incidence-inferred approach.
The first step is to fit this model, giving a posterior distribution for $\vec{P}$.

The second step is to transform the posterior distribution for $\vec{P}$ to a posterior distribution for $\vec{Z}$.
A posterior sample for $\vec{P}$ can be transformed to a posterior sample for $\vec{Z}$ based on \cref{E-inc-prev:eq:forward-substitute}, see \cref{backcalc:sec:methods} for details.

@@

The incidence-inferred approach is more parsimonious in being a single step procedure.
However, it poses several pragmatic challenges which means I favour the prevalence-inferred approach.
Here I explain that further developments, beyond the scope of this thesis, would be required to use the incidence-inferred approach within the computational constraints of the SRS.

It will be convenient to define a variable equating to the posterior initially estimated.
Let $\pi_{i,t} = Z_{i,t}$ under the inference-inferred approach and $\pi_{i,t} = P_{i,t}$ is the prevalence.

The chosen approach should have the following properties.
\begin{enumerate}
    \item The prior should favour $\pi_{i,t}$ changing exponentially in $t$, \ie penalize changes from exponential growth.
        % Penalizing changes from continuous exponential growth is a natural formulation because mechanistic models predict exponential growth over short periods of time.
        Such penalization has previously been shown to improve estimates of SARS-CoV-2 prevalence by balancing over and under-fitting~\autocite{ealesAppropriately} and is the approach used for the CIS prevalence model (see \cref{E-biology-data:sec:MRP}).
    \item Limit estimates to epidemiologically and biologically plausible values.
        That is, incidence proportion and prevalence should be in the interval $[0, 1]$.
        % While incidence proportion can theoretically be greater than 1, this would imply that some individuals were infected multiple times in a day which is not biologically plausible.
    \item Have sufficient parameters to incorporate all necessary covariates to correct for non-response bias.
    \item Borrow information across the different covariates.
        The borrowing should penalize changes in the distribution of incidence/prevalence across strata in the same geographic region being constant.
        A constant distribution is predicted by the theoretical study of epidemics, for example the dynamics of stratified, mechanistic transmission models (such as the one introduced in \cref{E-SEIR:sec:structured-populations}) over short periods of time with negligible behavioural and immunity changes.
    \item Be computationally efficient.
        The model will be fit to granular data and therefore needs to be run within the SRS, with its computational limitations (see \cref{E-biology-data:sec:SRS}).
\end{enumerate}

A parsimonious model satisfying properties 1 and 2 is to specify $\logit(\pi_{i,t}) = g_\varphi(i, t)$, where $g$ is a function parameterised by $\varphi$ and the prior on $\varphi$ is specified to favour $d^2g/dt^2 = 0$, \ie favour linear growth in $\logit(\pi_{i,t}$.
The prior $F_Z$ or $F_P$ is now a prior on $\varphi$.
The $\logit$ link function both limits $\pi_{i,t}$ to the interval $[0, 1]$, and logit-linear growth approximates exponential growth for small $\pi_{i,t}$~\autocite{ealesAppropriately}.

The logit transformation also allows property 4 to be conveniently satisfied using an additive model for $g_\varphi$.
An additive model on the logit scale is multiplicative on the natural scale for the small values of $\pi_{i,t}$ which will be common.

This form of model includes the MRP prevalence model in \cref{E-biology-data:sec:MRP}.

% Combined with property 4, the form of $g$ the null model is $g_\varphi(i, t) = \varphi_0 + \varphi_1 t + f(i)$ where $a_0$ and $a_t$ are model parameters and $f$ is a function to be specified; that is, changes away from this model should be penalized.

@@

INLA-based inference can only be applied to LGMs (\emph{Latent Gaussian Models}); see \cref{E-transmission:sec:INLA} for further details on INLA and LGMs.
The LGM framework requires that a transformation of $P_{i,t}$ is linear in $g_\varphi = \logit(\phi_{i,t})$.

If $\pi_{i,t} = P_{i,t}$ then this is trivially satisfied.
However, if $\pi_{i,t} = Z_{i,t}$, then no such linear relationship exists.
In particular:
\begin{align}
    P_{i,t}
    &= \sum_{k=0}^{\dmax} \pi_{i,t-k} S(k+1) \\
    &= \sum_{k=0}^{\dmax} \expit(g_\varphi(i, t-k)) S(k+1).
\end{align}

Therefore, satisfying all the desirable properties requires the prevalence-inferred approach, which I adopt.

\todo[inline]{Here to the end of the section moved to Appendix.}

@@

@@

Now I explain how I extended the MRP model introduced in \cref{E-biology-data:sec:MRP} to implement the prevalence-inferred approach.
I start with the prevalence posterior from \cref{E-biology-data:sec:positivity-results}, denoting the times the estimates are for as $t = 1, \dots, T$.
I draw 500 prevalence time series in each stratum from the approximate posterior distribution (using the procedure described in \cref{transmission:sec:INLA:posterior}).

Then, I transform this posterior sample using \cref{transmission:alg:calculate-Z}.
The algorithm is based on \cref{E-inc-prev:eq:forward-substitute}, which is repeated here for convenience:
\begin{align}
Z_t
% &= \frac{P_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= P_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{transmission:eq:forward-substitute}
\end{align}
Dividing each side of \cref{transmission:eq:forward-substitute} by the total number of individuals in each stratum transforms the number of prevalent individuals to prevalence and incidence to incidence proportion.
The algorithm uses a deterministic relationship between incidence and prevalence within a stratum, as \cref{E-inc-prev:sec:observation-process} justifies; \ie, the estimate of the incidence is negligibly affected by approximating the distribution $\vec{P} \mid \vec{Z}$ by its mean.

\begin{algorithm}
    \For{$j = 1, \dots, 500$}{
      Set $\vec{P}^{(j)}$ to a posterior sample of $\vec{P}$ \;
      \For{each stratum $i$}{
        \For{$t = -\dmax, \dots, 0$}{
            $Z^{(j)}_{i,t} = P^{(j)}_{i,1} / \sum_{k=1}^{\dmax} S(k)$
        }
        \For{$t = 1, \dots, T$}{
            Set $Z^{(j)}_{i,t} = P^{(j)}_{i,t} - \sum_{k=-\dmax}^{t-1} S(t - k + 1) Z^{(j)}_{i,k}$ \;
        }
      }
    }
    \caption{%
      Algorithm to transform 500 posterior samples posterior samples of $\vec{P}$ to posterior samples of $\vec{Z}$.
      Assumes constant incidence for $t \leq 1$ where $t = 1$ is the first day of prevalence data.
      Calculation of $Z^{(j)}_{i,t}$ is from \cref{transmission:eq:forward-substitute}.
    }
    \label{transmission:alg:calculate-Z}
\end{algorithm}

\Cref{transmission:eq:forward-substitute} is derived from \cref{E-inc-prev:eq:EPt-matrix}: $\vec{P} = \matr{S} \vec{I}$.
For this to have a unique solution, $\vec{I}$ and $\vec{P}$ need the same dimension.
However, I am using a period of prevalence which starts after the first infections.
These prior infections will still contribute to the prevalence.
I assume that the incidence for $t \leq 1$ is constant.
Therefore, $P_1 = I_0 \sum_{i=1}^{\dmax} S(i)$ and $I_t = P_1 / \sum_{i=1}^{\dmax} S(i)$ for $t \leq 1$.

% First, I draw a sample of 500 prevalence time series in each stratum from the approximate posterior distribution (using the procedure described in \cref{transmission:sec:INLA:posterior}).
% For each sample and stratum, I use the relationship in \cref{E-inc-prev:eq:EPt} to calculate the incidence proportion at each time point.
% I consider the relationship between incidence and prevalence within a stratum to be deterministic, as \cref{E-inc-prev:sec:observation-process} justifies, that is the estimate of the incidence is negligibly affected by approximating the distribution $\vec{P} \mid \vec{Z}$ by its mean.
% I solve this system using forward substitution, calculating the value of $Z_t$ in \cref{E-inc-prev:eq:forward-substitute} sequentially for $t = 1, \dots, T$.
% $t = 1$ is defined as the first day where prevalence data is used.
% \Cref{E-inc-prev:eq:forward-substitute} is repeated here for convenience:
% \begin{align}
% Z_t
% &= \frac{P_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
% &= P_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
% \label{transmission:eq:forward-substitute}
% \end{align}
% % \Cref{E-inc-prev:eq:EPt}, considered across different values of $t$, can be written as $\vec{P} = \matr{S} \vec{Z}$, where: $\vec{P}$ is a vector of the number of prevalent individuals at each time point in the stratum; $\matr{S}$ is a matrix formed from the survival function, as defined below; and $\vec{Z}$ is a vector of the incidence at each time point in the stratum.
% Dividing each side by the total number of individuals in each stratum transforms the number of prevalent individuals to prevalence and incidence to incidence proportion.

Violation of assumptions in various parts of this procedure can lead to the second term in \cref{transmission:eq:forward-substitute} to be greater than the first, giving negative incidence.
In this case, the incidence prior to day $t$ imply that the prevalence on day $t$ is higher than that predicted by the fitted regression model for this strata/day combination.
There are two sets of assumptions which are most likely to be violated.

The first set of assumptions is in estimating the survival function, $S(t)$, which is assumed to be known with no uncertainty in this procedure.
However, \cref{E-imperf-test} showed that the estimate of $S(t)$ is sensitive to assumptions made, such as the assumed $\psens$ and strength of priors used.

The second set of assumptions are in specifying the prior for $\vec{P}$.
In particular, the prior places non-zero mass on prevalence values which imply negative incidence under the other model assumptions.
Rectifying this assumption is challenging without switching to the inference-inferred approach, discussed further in \cref{backcalc:sec:results}.

For each posterior sample of $\vec{Z}$, I poststratify it to the CIS target population and subpopulations of interest.
This is done for each posterior sample using the methodology explained in \cref{E-biology-data:sec:MRP}.
The poststratified posterior samples are now posterior samples from the posterior of interest.

@@

During November, incidence starts rising, with regional heterogeneity in the timing of when this occurs (see \cref{transmission:fig:backcalc-regions}).
The most explored explanation for this is the emergence of the Alpha variant, which was more transmissible than previous variants and emerged at different times across the country~\autocite{walkerTracking,daviesEstimated,lythgoeLineage}.
There is evidence that when incidence starts increasing is correlated with when the Alpha variant's spread (see \cref{transmission:fig:backcalc-alpha}).
A second peak occurs in late December or early January in all regions; this second peak is larger than the first in all regions except the Northern three (North East, North West, and Yorkshire and the Humber).
\begin{figure}
    \todo[inline]{Make figure backcalc-regions easier to read}
    \includegraphics{transmission/backcalc-regions}
    \caption[Incidence estimated using backcalculation by region]{%
        Incidence proportion for all of England (A) and its component regions.
        Regions are split into broad groupings of three regions each: Northern (B), Midlands (C), and Southern (D).
        Yorkshire and the Humber is labelled as Yorkshire for brevity.
    }
    \label{transmission:fig:backcalc-regions}
\end{figure}
\begin{figure}
    \includegraphics{transmission/backcalc-alpha}
    \caption[Correlation of the emergence of Alpha and minimum incidence.]{%
        x-axis: time that S-gene target failure, a marker of the Alpha variant, is estimated to start increasing from baseline by region among CIS test results; from \textcite[table S3]{walkerTracking}.
        y-axis: posterior median and 95\% CrI of the date of minimum incidence in November or early December in each region.
        Linear regression line shown.
    }
    \label{transmission:fig:backcalc-alpha}
\end{figure}

@@

Various alternative inference techniques could be considered.
If the infection process is considered a Poisson process (defined in \cref{E-inc-prev:sec:poisson-process}), then, conditional on the process's intensity, there is independence between individuals' infection status.
The conditional independence implies the incidence proportion and prevalence are the mean of many independent Bernoulli variables.
Therefore, the Central Limit Theorem implies they are approximately normally distributed.
Exploiting this property could enable efficient approximations to the posterior.
For example, a Laplace approximation or variational inference~\autocite{bleiVariational}.
These methods require further work to check the quality of the approximations in this context.
